Project Proposal for Genetic Algorithms and Evolutionary Programming

### 2018-12-04 project_proposal/pp.tex
Small cosmetic fixes

We implemented our own very bot to act as an initial trainer for the network. This trainer is easier to defeat and even gives up after a certain amount of touches with the ball such that normal gameplay will be rewarded.
The simplification gives the evolutionary algorithm the opportunity to start optimizing the neural network in a valid direction, without introducing additional factors to the fitness score.

>>>>

We implemented our own bot to act as an initial trainer for the network. This trainer is easier to defeat and even gives up after a certain amount of touches with the ball, such that normal gameplay will be rewarded.
The simplification gives the evolutionary algorithm the opportunity to start optimizing the neural network in a valid direction, without introducing additional factors to the fitness score.
